---
title: "Accessing Kolada API"
author: "Eleftheria Chatzitheodoridou, Salvador Marti Roman"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
  toc: true
vignette: >
  %\VignetteIndexEntry{Accessing Kolada API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE
)
```

```{r, include = FALSE}
library(httr)
library(jsonlite)
library(AdvancedRlab5)
```

# About the Kolada API

The Kolada API provides a web-service that accesses Key Performance Indicators (KPI) of Swedish municipalities and organizational units. The open source database gives user access to approximately 5.000 figures, which can be useful for data analysis. Within the database we can find two types of data:

1. Municipal data

2. Organizational unit data

A detailed description can be found on the following website: <https://github.com/Hypergene/kolada/blob/master/README.rst>

```{r echo = FALSE}
library(httr)
library(jsonlite)

# Modified template from Best Practices for API Packages 
# https://cran.r-project.org/web/packages/httr/vignettes/api-packages.html

kolada_api <- function(path) {
  
  #Add v2 to path
  path = paste("v2/",path,sep="")
  url <- modify_url("http://api.kolada.se/v2/", path = path)
  
  #Check response format is json
  resp <- GET(url)
  print(resp)
  if (http_type(resp) != "application/json") {
    stop("API did not return json", call. = FALSE)
  }
  
  #Json parser
  parsed <- jsonlite::fromJSON(content(resp, "text"), simplifyVector = FALSE)
  
  # Check Response OK
  if (status_code(resp) != 200) {
    stop(
      sprintf(
        "Kolada API request failed [%s]\n%s\n<%s>", 
        status_code(resp),
        parsed$message,
        parsed$documentation_url
      ),
      call. = FALSE
    )
  }
  
  #Return a useful object
  structure(
    list(
      content = parsed,
      path = path,
      response = resp
    ),
    class = "kolada_api"
  )
}

get_municipality = function(name){
  stopifnot(is.character(name))
  stopifnot(!grepl("/",name, fixed=TRUE)) # checking if a string is in another string
  
  name = URLencode(name)
  response = kolada_api(paste("municipality?title=",name,sep=""))
  return(response$content)
}


get_municipality_groups = function(name){
  stopifnot(is.character(name))
  stopifnot(!grepl("/",name, fixed=TRUE))
  
  name = URLencode(name)
  response = kolada_api(paste("municipality?ou=",name,sep=""))
  return(response$content)
}

get_kpi = function(name){
  
  stopifnot(is.character(name))
  stopifnot(!grepl("/",name, fixed=TRUE))
  
  name = URLencode(name)
  response = kolada_api(paste("kpi?title=",name,sep=""))
  return(response$content)
}

get_kpi_groups = function(name){
  
  stopifnot(is.character(name))
  stopifnot(!grepl("/",name, fixed=TRUE))
  
  name = URLencode(name)
  response = kolada_api(paste("kpi_groups?title=",name,sep=""))
  return(response$content)
}

get_search_results = function(kpi_list=NULL, municipality_list=NULL,year_list=NULL){
  
  params = list(kpi=kpi_list,
             municipality=municipality_list,
             year=year_list)
  
  #Filter unused arguments
  params[sapply(params, is.null)] = NULL
  
  #Input checking
  sapply(params, function(x) stopifnot(is.list(x)))
  
  #Translate R term list into api term list
  search_terms = sapply(params, function(x) paste(x,collapse=","))
  
  #Build path from search terms
  path = paste(lapply(names(search_terms), function(x) paste(x,search_terms[x], sep="/"))
        ,collapse = "/")
  
  response = kolada_api(paste("data/", path,sep=""))
  return(response$content)
}

# Examples for testing:
# a = get_municipality("lund")
# b = get_municipality_groups("skola")
# c = get_kpi("Män som tar ut tillfällig föräldrapenning")
# d = get_kpi_groups("kostnad")
# e = get_search_results("add example pls")
```